---
title: "Fact and Fiction about STAT 250"
format: 
  revealjs:
    theme: moon
    slide-number: c/t
    show-slide-number: all
execute: 
  echo: false
  warning: false
---

```{r}
#| label: packages
library(tidyverse)
```

```{r}
#| label: read-data
stat250 <- read_csv("data_stat250/stat250_ay2324_deid.csv")
iar_250 <- read_csv("data_stat250/iar250_history.csv")
```


```{r}
#| label: data-cleaning
stat250_update <- stat250 |>
  filter(!crse_grade_off %in% c("IC", "AU", "I")) |>
  mutate(stat250_grade_group = case_when(
    crse_grade_off %in% c(
      "A", "A-", "A+", "B",
      "B+", "B-", "C", "C+", "C-", "CR"
    ) ~ "Passed STAT 250",
    crse_grade_off %in% c("D", "D+", "D-", "F", "NC") ~ "Did Not Pass STAT 250",
    crse_grade_off %in% c("W", "WU") ~ "Did Not Complete STAT 250"
  )) |>
  mutate(stat250_support_grade_group = case_when(
    crse_grade_off_support %in% c(
      "A", "A-", "A+", "B",
      "B+", "B-", "C", "C+", "C-", "CR"
    ) ~ "Passed Support",
    crse_grade_off_support %in% c("D", "D+", "D-", "F") ~ "Did Not Pass Support",
    crse_grade_off_support %in% c("W", "I", "IC", "WU") ~ "Did Not Complete Support"
  ))
```



## First Facts

- Your instructor wants you to be successful!  
- There is at least 15 hours of supplemental support available each week.  
- Your instructor is one of those resources (e.g. regular office hours, emails, appointments)

## Myth 1: Most students fail STAT 250

**Fact: 75% of students pass STAT 250 on their first attempt, with 70% of students passing each semester on average.**  

```{r}
#| label: pass-rate-graph
#| fig-align: center
iar_250 |>
  filter(acad_year %in% c(2022:2024)) |>
  filter(!crse_grade_off %in% c("IC", "AU", "I")) |>
  mutate(term_descr = fct_reorder(term_descr, strm)) |>
  mutate(stat250_grade_group = case_when(
    crse_grade_off %in% c(
      "A", "A-", "A+", "B",
      "B+", "B-", "C", "C+", "C-", "CR"
    ) ~ "Passed STAT 250",
    crse_grade_off %in% c("D", "D+", "D-", "F", "NC") ~ "Did Not Pass STAT 250",
    crse_grade_off %in% c("W", "WU") ~ "Did Not Complete STAT 250"
  )) |>
  filter(stat250_grade_group != "Did Not Complete STAT 250") |>
  count(stat250_grade_group, acad_year) |>
  group_by(acad_year) |>
  mutate(prop_pass = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(x = prop_pass, y = fct_rev(factor(acad_year)), fill = stat250_grade_group)) +
  geom_col(position = "stack") +
  geom_vline(xintercept = 0.70) +
  theme_light() +
  theme(legend.position = "bottom") +
  scale_fill_viridis_d() +
  labs(
    x = "Proportion of First-Time STAT 250 Students",
    y = "Academic Year",
    fill = "Outcome"
  )
```

::: {style="font-size:50%"}

For comparison,  

- BIO 311 Genetics has a 56% pass rate  
- Anatomy and Physiology has a 71% pass rate  
- CHEM 111 Chemistry II has a 71% pass rate

:::

## Myth 2: Half the students are repeating the course each semester

**Fact: Each semester, on average, 80% of students are taking STAT 250 for the first time**

```{r}
#| label: first-time-graph
#| fig-align: center
iar_250 |>
  filter(acad_year %in% c(2022:2024)) |>
  filter(!crse_grade_off %in% c("IC", "AU", "I")) |>
  mutate(term_descr = fct_reorder(term_descr, strm)) |>
  mutate(stat250_grade_group = case_when(
    crse_grade_off %in% c(
      "A", "A-", "A+", "B",
      "B+", "B-", "C", "C+", "C-", "CR"
    ) ~ "Passed STAT 250",
    crse_grade_off %in% c("D", "D+", "D-", "F", "NC") ~ "Did Not Pass STAT 250",
    crse_grade_off %in% c("W", "WU") ~ "Did Not Complete STAT 250"
  )) |>
  count(term_descr, attempt_number) |>
  group_by(term_descr) |>
  mutate(prop_attempt = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(x = prop_attempt, y = fct_rev(term_descr), fill = fct_rev(factor(attempt_number)))) +
  geom_col(position = "stack") +
  theme_light() +
  theme(legend.position = "bottom") +
  scale_fill_viridis_d() +
  labs(
    title = "On average, 80% of students in STAT 250 are on their first attempt",
    x = "Proportion of Students Per Attempt",
    y = "Semester",
    fill = "Attempt"
  )
```





## Myth 3: One Instructor is Harder than the Other

**Fact: For students on their first attempt, the pass rates are consistent across instructors**

```{r}
#| label: instructor-comparison-graph
#| fig-align: center
iar_250 |>
  filter(acad_year %in% c(2020:2024)) |>
  filter(!crse_grade_off %in% c("IC", "AU", "I")) |>
  filter(attempt_number == 1) |>
  mutate(term_descr = fct_reorder(term_descr, strm)) |>
  mutate(stat250_grade_group = case_when(
    crse_grade_off %in% c(
      "A", "A-", "A+", "B",
      "B+", "B-", "C", "C+", "C-", "CR"
    ) ~ "Passed STAT 250",
    crse_grade_off %in% c("D", "D+", "D-", "F", "NC") ~ "Did Not Pass STAT 250",
    crse_grade_off %in% c("W", "WU") ~ "Did Not Complete STAT 250"
  )) |>
  filter(stat250_grade_group != "Did Not Complete STAT 250") |>
  count(pri_instr_emplid, stat250_grade_group) |>
  group_by(pri_instr_emplid) |>
  mutate(prop_pass = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(x = prop_pass, y = pri_instr_emplid, fill = stat250_grade_group)) +
  geom_col(position = "stack") +
  theme_light() +
  theme(legend.position = "bottom") +
  # facet_wrap(~term_descr) + #add term_desrc to count and group_by to add in
  # geom_vline(xintercept = 0.70) +
  scale_fill_viridis_d() +
  labs(
    x = "Proportion of First-Time STAT 250 Students",
    y = "Instructor",
    fill = "Outcome"
  ) +
  scale_y_discrete(labels = c("E", "D", "C", "B", "A"))
```

## Myth 4: STAT 250 has a higher workload than other classes

::: {.r-fit-text}

- Remember that STAT 250 is a 4-unit course.  
- 8-12 hours of work outside the classroom is normal for a 4-unit college-level class  
- Outside work includes both assignments for the class (e.g. preps, labs) and review/study time  

:::

## Myth 4: STAT 250 has a higher workload than other classes

**Fact: Lab Assignments should take you on average 5 hours each assignment**  
```{r}
#| label: workload-labs-graph
#| fig-align: center
pass_labs <- stat250_update |>
  mutate(time_labs = fct_relevel(time_labs, "10+ hours avg per week", after = Inf)) |>
  drop_na(time_labs) |>
  count(time_labs, stat250_grade_group) |>
  group_by(time_labs) |> 
  mutate(prop_pass_labs = round(n/sum(n)*100, 0),
         group_total = sum(n)) |> 
  ungroup() |> 
  filter(stat250_grade_group == "Passed STAT 250")

stat250_update |>
  mutate(time_labs = fct_relevel(time_labs, "10+ hours avg per week", after = Inf)) |>
  drop_na(time_labs) |>
  count(time_labs) |>
  ggplot(aes(
    x = n, y = time_labs,
    fill = time_labs
  )) +
  geom_col() +
  geom_text(data = pass_labs, 
            aes(label = paste0(prop_pass_labs, "% Passed"),
                x = 6)) +
  guides(fill = "none") +
  scale_fill_viridis_d(begin = 0.15) +
  theme_light() +
  labs(
    x = "Number of STAT 250 Students in AY 2023-2024",
    y = "Reported Time Spent Each Week",
    title = "Reported Time Spent Each Week On \n Lab Assignments"
  ) +
  theme(plot.title = element_text(hjust = 0.5))

```



## Myth 4: STAT 250 has a higher workload than other classes

::: {.r-fit-text}

If you are spending more time than 5 hours on the labs, especially after the first 3 weeks, please start them early and seek help often!  

A few tips:  

- Start labs at the Friday or Monday Cafe to get going  
- Try to work on labs one hour each day  
- Use CLC Drop-In Hours, Instructor Office Hours, and the Wednesday Cafe to ask questions long the way  
- If an error message is holding you up
    - Take a break and go for a walk so you can look at it with fresh eyes  
    - Check for common issues (spelling, capitalization, missing commas, missing parentheses)  
    - Check you loaded the correct packages and imported the data  
    - Email your instructor with a screen shot of code and the error   
    
:::






## Myth 4: STAT 250 has a higher workload than other classes

::: {.r-fit-text}
**Fact: Checkpoints preparation includes practice problems and review, but they are meant to be low-stakes assessments**  

1-2 hours a week on average (maybe 2-3 if you need more practice) is a good target for Checkpoint preparation.  

:::

```{r}
#| label: workload-checkpoints-graph
#| fig-align: center
pass_checkpoints <- stat250_update |>
  filter(time_checkpoints != "I did not do this assignment most weeks") |> 
  mutate(time_checkpoints = fct_relevel(time_checkpoints, "10+ hours avg per week", after = 8),
         stat250_grade_group = as.factor(stat250_grade_group)) |>
  drop_na(time_checkpoints) |>
  count(time_checkpoints, stat250_grade_group, .drop = FALSE) |>
  group_by(time_checkpoints) |> 
  mutate(prop_pass_checkpoints = round(n/sum(n)*100, 0),
         group_total = sum(n)) |> 
  ungroup() |> 
  filter(stat250_grade_group == "Passed STAT 250")

stat250_update |>
  filter(time_checkpoints != "I did not do this assignment most weeks") |>
  mutate(time_checkpoints = fct_relevel(time_checkpoints, "10+ hours avg per week", after = 8)) |>
  drop_na(time_checkpoints) |>
  count(time_checkpoints) |>
  ggplot(aes(
    x = n, y = time_checkpoints,
    fill = time_checkpoints
  )) +
  geom_col() +
  geom_text(data = pass_checkpoints, 
            aes(label = paste0(prop_pass_checkpoints, "% Passed"),
                x = 13)) +
  guides(fill = "none") +
  scale_fill_viridis_d(begin = 0.15) +
  theme_light() +
  labs(
    x = "Number of STAT 250 Students in AY 2023-2024",
    y = "Reported Time Spent Each Week",
    title = "Reported Time Spent Each Week On \n Checkpoint Preparation"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```


## Myth 4: STAT 250 has a higher workload than other classes {.scrollable}

::: {.r-fit-text}

**Fact: Each Prep Assignment ranges in time between 20-60 minutes for the videos plus your time on the reflection questions**  

Reflection after you watch the videos before class and reflection after class to update your understanding are both important aspects of the reflection preparation

:::

```{r}
#| label: workload-preps-fa23
#| fig-align: center
pass_preps_fall2023 <- stat250_update |>
  filter(time_preps != "I did not do this assignment most weeks") |> 
  mutate(time_preps = fct_relevel(time_preps, "10+ hours avg per week", after = Inf),
         stat250_grade_group = as.factor(stat250_grade_group)) |>
  drop_na(time_preps) |>
  count(time_preps, stat250_grade_group, .drop = FALSE) |>
  group_by(time_preps) |> 
  mutate(prop_pass_prep = round(n/sum(n)*100, 0),
         group_total = sum(n)) |> 
  ungroup() |> 
  filter(stat250_grade_group == "Passed STAT 250")


time_preps_fall2023 <- stat250_update |>
  mutate(time_preps = fct_relevel(time_preps, "10+ hours avg per week", after = Inf)) |>
  drop_na(time_preps) |>
  count(time_preps) |>
  ggplot(aes(
    x = n, y = time_preps,
    fill = time_preps
  )) +
  geom_col() +
  geom_text(data = pass_preps_fall2023, 
            aes(label = paste0(prop_pass_prep, "% Passed"),
                x = 7)) +
  guides(fill = "none") +
  scale_fill_viridis_d(begin = 0.2) +
  theme_light() +
  labs(
    x = "Number of STAT 250 Students in Fall 2023",
    y = "Reported Time Spent Each Week",
    title = "Reported Time Spent Each Week On \n Preparation Assignments"
  ) +
  theme(plot.title = element_text(hjust = 0.5))

time_preps_fall2023
```



```{r}
#| label: workload-prep-video-sp24
#| fig-align: center
pass_preps_sp24_vids <- stat250_update |>
  mutate(stat250_grade_group = as.factor(stat250_grade_group)) |>
  drop_na(time_preps_video) |>
  count(time_preps_video, stat250_grade_group, .drop = FALSE) |>
  group_by(time_preps_video) |> 
  mutate(prop_pass_prep_vid = round(n/sum(n)*100, 0),
         group_total = sum(n)) |> 
  ungroup() |> 
  filter(stat250_grade_group == "Passed STAT 250")


stat250_update |>
  drop_na(time_preps_video) |>
  count(time_preps_video) |>
  ggplot(aes(
    x = n, y = time_preps_video,
    fill = time_preps_video
  )) +
  geom_col() +
  geom_text(data = pass_preps_sp24_vids, 
            aes(label = paste0(prop_pass_prep_vid, "% Passed"),
                x = 7)) +
  guides(fill = "none") +
  scale_fill_viridis_d(begin = 0.2) +
  theme_light() +
  labs(
    x = "Number of STAT 250 Students in Spring 2024",
    y = "Reported Time Spent Each Week",
    title = "Reported Time Spent Each Week On \n Preparation Videos"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
#| label: workload-prep-reflect-sp24
#| fig-align: center
pass_preps_sp24_reflect <- stat250_update |>
  mutate(stat250_grade_group = as.factor(stat250_grade_group)) |>
  drop_na(time_preps_reflections) |>
  count(time_preps_reflections, stat250_grade_group, .drop = FALSE) |>
  group_by(time_preps_reflections) |> 
  mutate(prop_pass_prep_ref = round(n/sum(n)*100, 0),
         group_total = sum(n)) |> 
  ungroup() |> 
  filter(stat250_grade_group == "Passed STAT 250")


stat250_update |>
  drop_na(time_preps_reflections) |>
  count(time_preps_reflections) |>
  ggplot(aes(
    x = n, y = time_preps_reflections,
    fill = time_preps_reflections
  )) +
  geom_col() +
  geom_text(data = pass_preps_sp24_reflect, 
            aes(label = paste0(prop_pass_prep_ref, "% Passed"),
                x = 7)) +
  guides(fill = "none") +
  scale_fill_viridis_d(begin = 0.2) +
  theme_light() +
  labs(
    x = "Number of STAT 250 Students in Spring 2024",
    y = "Reported Time Spent Each Week",
    title = "Reported Time Spent Each Week On \n Preparation Reflections"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```




## Myth 4: STAT 250 has a higher workload than other classes 

::: {.r-fit-text}
For most students, the average weekly workload (weighted by pass rate) was  

- Labs: 5-6 hours a week
- Checkpoints: 1-2 hours a week  
- Prep Videos: 1-2 hours a week  
- Prep Reflections: 2-3 hours a week 

Total: 10-13 hours a week

:::




## Hard Truth: Students who are repeating are more likely not to pass

```{r}
#| label: pass-rate-repeats-graph
#| fig-align: center
iar_250 |>
  filter(acad_year %in% c(2022:2024)) |>
  filter(!crse_grade_off %in% c("IC", "AU", "I")) |>
  mutate(term_descr = fct_reorder(term_descr, strm)) |>
  mutate(stat250_grade_group = case_when(
    crse_grade_off %in% c(
      "A", "A-", "A+", "B",
      "B+", "B-", "C", "C+", "C-", "CR"
    ) ~ "Passed STAT 250",
    crse_grade_off %in% c("D", "D+", "D-", "F", "NC") ~ "Did Not Pass STAT 250",
    crse_grade_off %in% c("W", "WU") ~ "Did Not Complete STAT 250"
  )) |>
  mutate(repeater = ifelse(attempt_number == 1, "First-Time", "Repeating")) |>
  count(stat250_grade_group, repeater) |>
  group_by(repeater) |>
  mutate(prop_passed = n / sum(n)) |>
  ungroup() |>
  ggplot(aes(x = prop_passed, y = fct_rev(repeater), fill = stat250_grade_group, label = n)) +
  geom_col(position = "stack") +
  theme_light() +
  theme(legend.position = "bottom") +
  scale_fill_viridis_d() +
  labs(
    title = "Students who repeat are more likely not to pass",
    x = "Proportion of Students Per Outcome",
    y = "Student Attempt at STAT 250",
    fill = "Outcome"
  )
```


## Hard Truth: Students who worked more than 10 hours a week are more likely not to pass

```{r}
#| label: avg-work-hours
#| eval: false
#| fig-align: center
stat250_update |>
  mutate(grade_group = case_when(
    crse_grade_off %in% c("A", "A-", "A+") ~ "A",
    crse_grade_off %in% c("B", "B-", "B+") ~ "B",
    crse_grade_off %in% c("C", "C-", "C+") ~ "C",
    crse_grade_off %in% c("D", "D-", "D+", "NC", "F") ~ "Did not Pass",
    crse_grade_off %in% c("W", "WU", "I", "IC") ~ "W/WU",
    crse_grade_off == "CR" ~ "CR"
  )) |>
  filter(
    grade_group != "W/WU",
    term_descr == "2024 Spring"
  ) |>
  filter(attempt_number == 1) |>
  group_by(grade_group) |>
  summarize(avg_work = mean(work_hours, na.rm = TRUE))
```


```{r}
#| label: pass-rate-work-hours-graph
#| fig-align: center
stat250_update |>
  mutate(grade_group = case_when(
    crse_grade_off %in% c("A", "A-", "A+") ~ "A",
    crse_grade_off %in% c("B", "B-", "B+") ~ "B",
    crse_grade_off %in% c("C", "C-", "C+") ~ "C",
    crse_grade_off %in% c("D", "D-", "D+", "NC", "F") ~ "Did not Pass",
    crse_grade_off %in% c("W", "WU", "I", "IC") ~ "W/WU",
    crse_grade_off == "CR" ~ "CR"
  )) |>
  filter(
    grade_group != "W/WU",
    term_descr == "2024 Spring"
  ) |>
  filter(attempt_number == 1) |>
  ggplot(aes(x = work_hours, y = fct_rev(grade_group))) +
  geom_boxplot(aes(fill = grade_group),
    alpha = 0.25
  ) +
  geom_point(aes(color = grade_group),
    position = position_jitter(height = 0.1)
  ) +
  guides(
    fill = "none",
    color = "none"
  ) +
  scale_fill_viridis_d() +
  scale_color_viridis_d() +
  theme_light() +
  labs(
    x = "Average Reported Hours of Work Per Week for First-Time STAT 250 Students",
    y = "Grade Group in STAT 250"
  )
```


## Hard Truth: Preparation before reaching STAT 250 impacts student success  

:::: {.columns}

::: {.column width="40%"}

::: {.r-fit-text}
- Students with lower high school GPAs are less likely to pass STAT 250  
- GPA does not necessarily measure ability; it is more often connected to study skill development 
- Most likely students who do not pass STAT 250 may need to develop more robust **STUDY SKILLS**  
:::

:::

::: {.column width="60%"}
```{r}
#| label: pass-rate-hsgpa-graph
#| fig-align: center
stat250_update |>
  mutate(grade_group = case_when(
    crse_grade_off %in% c("A", "A-", "A+") ~ "A",
    crse_grade_off %in% c("B", "B-", "B+") ~ "B",
    crse_grade_off %in% c("C", "C-", "C+") ~ "C",
    crse_grade_off %in% c("D", "D-", "D+", "NC", "F") ~ "Did not Pass",
    crse_grade_off %in% c("W", "WU", "I", "IC") ~ "W/WU",
    crse_grade_off == "CR" ~ "CR"
  )) |>
  filter(csu_co_hs_gpa <= 5 & csu_co_hs_gpa > 0) |>
  filter(grade_group != "W/WU") |>
  filter(attempt_number == 1) |>
  mutate(term_descr = fct_inorder(term_descr)) |>
  ggplot(aes(x = csu_co_hs_gpa, y = fct_rev(grade_group))) +
  geom_boxplot(aes(fill = grade_group),
    alpha = 0.25
  ) +
  geom_point(aes(color = grade_group),
    position = position_jitter(height = 0.1)
  ) +
  guides(
    fill = "none",
    color = "none"
  ) +
  scale_fill_viridis_d() +
  scale_color_viridis_d() +
  theme_light() +
  labs(
    x = "High School GPA for First-Time STAT 250 Students",
    y = "Grade Group in STAT 250"
  )
```
:::

::::

## How to Improve Your Study Skills 

- [Supplemental Instruction at the CLC](https://csumb.edu/clc/)  
- [Center for Student Success](https://csumb.edu/css/)  

**_Remember, test taking ability is not a fixed characteristic._** Check out [these strategies](https://www.edumed.org/resources/test-taking-strategies/) for exam preparation.  


## Hard Truth: How students seek help is as important as how often they seek help

:::: {.columns}

::: {.column width="40%"}

::: {.r-fit-text}
  
- You might expect the "Rarely" group to have lower pass rates, but that group is made up students with more preparation who may not need frequent help.  
- Students with less preparation and/or with less-developed study skills benefit more from regular help than occasional.  
:::

:::

::: {.column width="60%"}
```{r}
#| label: pass-rate-help-graph
#| fig-align: center
#| fig-height: 8
stat250_update |>
  mutate(grade_group = case_when(
    crse_grade_off %in% c("A", "A-", "A+") ~ "Pass A/B",
    crse_grade_off %in% c("B", "B-", "B+", "CR") ~ "Pass A/B",
    crse_grade_off %in% c("C", "C-", "C+") ~ "Pass C",
    crse_grade_off %in% c("D", "D-", "D+", "NC", "F") ~ "Did not Pass",
    crse_grade_off %in% c("W", "WU", "I", "IC") ~ "W/WU"
  )) |>
  filter(grade_group != "W/WU") |>
  filter(attempt_number == 1) |>
  mutate(term_descr = fct_inorder(term_descr)) |>
  mutate(help_attend_cafe = factor(help_attend_cafe, levels = c(
    "Never", "Once or twice",
    "Several times", "Regularly, about once per week",
    "More than once per week"
  ))) |>
  mutate(grade_group = factor(grade_group, levels = c("Did not Pass", "Pass C", "Pass A/B"))) |>
  mutate(help_attend_clc_dropin_num = parse_number(help_attend_clc_dropin),
         help_attend_clc_si_num = parse_number(help_attend_clc_si),
         help_attend_prof_office_num = parse_number(help_attend_prof_office),
         help_attend_study_group_num = parse_number(help_attend_study_group)) |> 
  rowwise() |> 
  mutate(avg_weekly_help_total = sum(c(help_attend_clc_dropin_num,
                                     help_attend_clc_si_num,
                                     help_attend_prof_office_num),
                                     na.rm = TRUE)) |> 
  mutate(help_frequency = case_when(avg_weekly_help_total == 0 & 
                                      help_attend_cafe %in% c("Never", "Once or twice") ~ "Rarely",
                                    avg_weekly_help_total >= 2 | 
                                      help_attend_cafe %in% c("Regularly, about once per week", 
                                                              "More than once per week") ~ "Regularly",
                                    TRUE ~ "Occasionally")) |> 
  # mutate(help_frequency = case_when(
  #   help_attend_cafe %in% c("Never", "Once or twice") &
  #     help_attend_clc_dropin %in% c("0") &
  #     help_attend_clc_si %in% c("0") &
  #     help_attend_prof_office %in% c("0") &
  #     help_attend_study_group %in% c("0") ~ "Rarely",
  #   help_attend_cafe %in% c("More than once per week"
  #   ) |
  #     help_attend_clc_dropin %in% c("2", "3", "4", "5 or more times") |
  #     help_attend_clc_si %in% c("2", "3", "4", "5 or more times") |
  #     help_attend_prof_office %in% c("2", "3", "4", "5 or more times") |
  #     help_attend_study_group %in% c("2", "3", "4", "5 or more times") ~ "Very Frequently",
  #   is.na(help_attend_cafe) &
  #     is.na(help_attend_clc_dropin) &
  #     is.na(help_attend_clc_si) &
  #     is.na(help_attend_prof_office) &
  #     is.na(help_attend_study_group) ~ "No Data",
  #   TRUE ~ "Regularly"
  # )) |>
  mutate(help_frequency = factor(help_frequency, levels = c("No Data", "Rarely", "Occasionally", "Regularly"))) |>
  mutate(prep_level = case_when(csu_app_mq_cat %in% c(1, 2) ~ "Prepared for College Math/Stat",
                                csu_app_mq_cat %in% c(3, 4) ~ "Underprepared for College Math/Stat")) |> 
  count(grade_group, help_frequency, prep_level) |>
  group_by(help_frequency, prep_level) |>
  mutate(
    prop_cafe = n / sum(n),
    group_total = sum(n)
  ) |>
  ungroup() |> 
  filter(group_total >= 10) |> 
  ggplot(aes(y = help_frequency, fill = grade_group)) +
  geom_col(aes(x = prop_cafe)) +
  facet_wrap(~prep_level, nrow = 2) +
  # geom_text(aes(label = group_total, x = 0.1)) +
  scale_fill_viridis_d() +
  theme_light() +
  theme(legend.position = "bottom") +
  labs(
    x = "Proportion of First-Time STAT 250 Students",
    y = "Frequency of Seeking Help",
    caption = "Help includes CLC, Office Hours, and Cafes \n Groups less than 10 excluded",
    fill = "STAT 250 Grade Group"
  )
```

:::

::::


## Hard Truth: How students seek help is as important as how often they seek help

::: {.r-fit-text}
Regularly seeking help (e.g. attending cafe weekly, CLC/Office Hours weekly, study groups) may improve the grades STAT 250 students, but it does not guarantee a passing grade. Why?    

- Students who seek regular help, but do not pass, are often working with other students in ways that do not support their learning  
    - Partnerships where one person does the majority of the work  
    - Partnerships where one person does not explain "why" something should be done one way or another  
    - Partnerships where one person does not ask questions when they are confused  
    - Partnerships where one person does not consider the confusion of others  
- Students also may frequently attend CLC Sessions Drop-Ins or Cafes, but do not ask questions or prepare in advance  

:::


## What can you do to be successful?  

- Don't wait to get help, start early and often  
- Evaluate your study habits, you can become a good test taker  
- Research [how people learn](https://mcgraw.princeton.edu/undergraduates/resources/resource-library/how-people-learn)  
- Practice [Mindfulness](https://www.mayoclinic.org/healthy-lifestyle/consumer-health/in-depth/mindfulness-exercises/art-20046356) to help with anxiety  
- Trust that we want your success  
